\begin{etaremune}

    %%% 2024 (1)
  
    \listpart{\centering\large\textbf{-- 2024 --}}
  
    \item M.~Zafar, \textbf{D.~Dutykh}, P.~Sabatier, M.~Banjan and J.~Kim. \textit{Uncovering a Paleotsunami Triggered by Mass-Movement in an Alpine Lake}. In: P.~Gourbesville, G.~Caignaert (Eds.) Advances in Hydroinformatics --- SimHydro 2023 Volume 2. SimHydro 2023. Springer Water. Springer, Singapore, pp.~47--64, 2024 \\ % Yes (HAL, Arxiv, RG)
    \url{https://hal.science/hal-04261487/}
  
    %%% 2022 (1)
  
    \listpart{\centering\large\textbf{-- 2022 --}}
    
    \item T.S.B.~Abd~Manan, T.~Khan, W.H.M.~Wan~Mohtar, A.~Machmudah, \textbf{D.~Dutykh}, S.~Qazi, A.~Ahmad and N.~Wan~Rasdi. \textit{Bioremediation of wastewater using algae for potential renewable bioenergy cogeneration}, In A.~Ahmad, F.~Banat and H.~Taher (Eds.) Algal Biotechnology: Integrated Algal Engineering for Bioenergy, Bioremediation, and Biomedical Applications, Elsevier, Amsterdam, pp.~47--62, 2022 % No (HAL & Arxiv)
  
    %%% 2021 (1)
  
    \listpart{\centering\large\textbf{-- 2021 --}}
    
    \item V.~Roubtsov and \textbf{D.~Dutykh}. \textit{Poisson and Symplectic structures, Hamiltonian action, momentum and reduction}, In M.~Ulan and E.~Schneider (Eds.) Differential Geometry, Differential Equations, and Mathematical Physics. Birkh\"auser, Cham, pp.~1--29, 2021 \\ % Arxiv
    \url{https://hal.archives-ouvertes.fr/hal-02522156/}
  
    %%% 2019 (1)
  
    \listpart{\centering\large\textbf{-- 2019 --}}
  
    \item T.~Torsvik, A.~Abdalazeez, \textbf{D.~Dutykh}, P.~Denissenko and I.~Didenkulova. \textit{Dispersive and non-dispersive nonlinear long wave transformations: numerical and experimental results}, In A.~\textsc{Berezovski} and T.~\textsc{Soomere} (Eds.) Applied Wave Mathematics II, Mathematics of Planet Earth, Vol.~\textbf{6}. pp.~41--66, Springer Cham, 2019 \\ % Arxiv
    \url{https://hal.archives-ouvertes.fr/hal-02289778/}
    
    %%% 2018 (1)
  
    \listpart{\centering\large\textbf{-- 2018 --}}
  
    \item A.~Dur\'an, \textbf{D.~Dutykh} and D.~Mitsotakis. \textit{Peregrine's system revisited}, In N.~\textsc{Abcha}, E.~\textsc{Pelinovsky} and I.~\textsc{Mutabazi} (Eds.) Nonlinear Waves and Pattern Dynamics, pp.~3--43, Springer Cham, 2018 \\ % Arxiv
    \url{https://hal.archives-ouvertes.fr/hal-01703491/}
    
    %%% 2016 (1)
  
    \listpart{\centering\large\textbf{-- 2016 --}}
  
    \item D.~Clamond and \textbf{D.~Dutykh}. \textit{Modeling water waves beyond perturbations}, in E.~\textsc{Tobisch} (Ed.): New Approaches to Nonlinear Waves, Lecture Notes in Physics (\textbf{908}), 197--210, Springer, 2016 \\ % Arxiv
    \url{https://hal.archives-ouvertes.fr/hal-01102120/}
    
    %%% 2014 (2)
  
    \listpart{\centering\large\textbf{-- 2014 --}}
  
    \item D.~Clamond and \textbf{D.~Dutykh}. \textit{A Non-Hydrostatic Non-Dispersive Shallow Water Model}, Ph.~\textsc{Goubersville}, J.~\textsc{Cunge}, G.~\textsc{Caignaert} (Eds.): Springer Hydrogeology. Advances in Hydroinformatics: SIMHYDRO 2012 --- New Frontiers of Simulation, 197--206, Springer Singapore 2014 \\ % No (Arxiv)
    \url{https://hal.archives-ouvertes.fr/hal-00907110/}
  
    \item V.~Guinot, D.~Clamond and \textbf{D.~Dutykh}. \textit{Finite Volume Implementation of Non-Dispersive, Non-Hydrostatic Shallow Water Equations}, Ph.~\textsc{Goubersville}, J.~\textsc{Cunge}, G.~\textsc{Caignaert} (Eds.): Springer Hydrogeology. Advances in Hydroinformatics: SIMHYDRO 2012 --- New Frontiers of Simulation, 189--196, Springer Singapore 2014 \\ % No (Arxiv)
    \url{https://hal.archives-ouvertes.fr/hal-00907108/}
    
    %%% 2011 (1)
  
    \listpart{\centering\large\textbf{-- 2011 --}}
  
    \item Y.~Meyapin, \textbf{D.~Dutykh} and M.~Gisclon. \textit{Two-fluid barotropic models for powder-snow avalanche flows}, E. Krause \emph{et al.} (Eds.): Computational Sci. \& High Performance Computing IV, NNFM 115, pp. 219--232. Springer-Verlag Berlin Heidelberg 2011 \\ % Arxiv
    \url{http://hal.archives-ouvertes.fr/hal-00394437/}
    
    %%% 2007 (1)
  
    \listpart{\centering\large\textbf{-- 2007 --}}
    
    \item \textbf{D.~Dutykh} and F.~Dias, \textit{Water waves generated by a moving bottom}. In book: ``Tsunami and Nonlinear Waves'', A.~\textsc{Kundu} (Editor), pp. 65--95, Springer Verlag 2007, Approx. 325 p., 170 illus., Hardcover, ISBN: 978-3-540-71255-8 \\ % Arxiv
    \url{http://hal.archives-ouvertes.fr/hal-00115875/}
    
    %%% 2006 (1)
  
    \listpart{\centering\large\textbf{-- 2006 --}}
    
    \item F.~Dias and \textbf{D.~Dutykh}. \textit{Dynamics of tsunami waves}. In Book: ``Extreme Man-Made and Natural Hazards in Dynamics of Structures'', A.~\textsc{Ibrahimbegovic} and I.~\textsc{Kozar} (Eds), Springer Dordrecht, NATO Advanced Research Workshop, Opatija, Croatia, May 28 --- June 1, pp. 35--60, 2006 \\ % Arxiv
    \url{http://hal.archives-ouvertes.fr/hal-00113612/}
    
  \end{etaremune}